---
title: "Microbial Signatures Data Munging"
package: MungeCuratedMGS
output:
  BiocStyle::html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
abstract: |
  Just data munging.
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Installation

```{r eval=FALSE}
BiocManager::install('seandavi/MungeCuratedMGS')
```

# Data entities

```{r message=FALSE, warning=FALSE}
library(MungeCuratedMGS)
```

# Authentication

Run only once to authenticate, before running vignette (not evaluated in vignette):
```{r eval=FALSE}
library(googlesheets)
token = gs_auth()
saveRDS(token, file = "/tmp/googlesheets_token.rds")
```

Then run with the vignette, each time:
```{r eval=FALSE}
library(googlesheets)
suppressMessages(gs_auth(token = "/tmp/googlesheets_token.rds", verbose = FALSE))
```


## Ontologies

### EFO

```{r efo, cache=TRUE, eval=FALSE}
efo = get_efo()
head(efo)
```

### UBERON

```{r uberon, cache=TRUE, eval=FALSE}
uberon = get_uberon()
head(uberon)
```

Ontologies can be combined like so:

```{r, eval=FALSE}
library(dplyr)
full_ontologies = dplyr::bind_rows(uberon, efo)
```

## NCBI Taxonomy

### Names and Taxon IDs

```{r taxon_names, cache=TRUE, eval=FALSE}
taxon_dir = get_taxon_dump_files()
taxon_id_names = get_taxon_names(taxon_dir)
head(taxon_id_names, 10)
```

## Write all curation tables as csv files

```{r}
sheet <- curation_sheet()
dim(sheet)
```

```{r}
study <- create_study_table(sheet)
signature <- create_signature_table(sheet)
```

Create keys and write to file:
```{r}
signature$Study <- create_keys("Study ", study)
signature$`Page Name` <- sort(create_keys("Signature ", signature))
study$`Page Name` <- create_keys("Study ", study)
study <- unique(study)
study <- study[order(study$`Page Name`), ]
write.csv(study, file="studies.csv", row.names = FALSE)
write.csv(signature, file="signatures.csv", row.names = FALSE)
```

Write the signatures file again, alternating metaphlan and NCBI columns:
```{r}
nonsigcols <- grep("Metaphlan|NCBI|Study|Page", colnames(signature), invert=TRUE)
sigcols <- as.integer(t(cbind(grep("Metaphlan", colnames(signature)), grep("NCBI", colnames(signature)))))
keys <- grep("Study|Page", colnames(signature))
signature2 <- signature[, c(nonsigcols, sigcols, keys)]
write.csv(signature2, file="signatures_alternatingNCBI.csv", row.names = FALSE)
```

