---
title: "Microbial Signatures Data Munging"
package: MungeCuratedMGS
output:
  BiocStyle::html_document:
    number_sections: yes
    toc: yes
    toc_depth: 4
abstract: |
  Just data munging.
vignette: |
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```

# Installation

```{r eval=FALSE}
BiocManager::install('seandavi/MungeCuratedMGS')
```

# Data entities

```{r message=FALSE, warning=FALSE}
library(MungeCuratedMGS)
```

# Authentication

Run only once to authenticate, before running vignette (not evaluated in vignette):
```{r eval=FALSE}
library(googlesheets)
token = gs_auth()
saveRDS(token, file = "/tmp/googlesheets_token.rds")
```

Then run with the vignette, each time:
```{r eval=FALSE}
library(googlesheets)
suppressMessages(gs_auth(token = "/tmp/googlesheets_token.rds", verbose = FALSE))
```


## Ontologies

### EFO

```{r efo, cache=TRUE}
efo = get_efo()
head(efo)
```

### UBERON

```{r uberon, cache=TRUE}
uberon = get_uberon()
head(uberon)
```

Ontologies can be combined like so:

```{r}
library(dplyr)
full_ontologies = dplyr::bind_rows(uberon, efo)
```

## NCBI Taxonomy

### Names and Taxon IDs

```{r taxon_names, cache=TRUE}
taxon_dir = get_taxon_dump_files()
taxon_id_names = get_taxon_names(taxon_dir)
head(taxon_id_names, 10)
```

## Curation Tables

### Signature metadata

```{r sig_table_from_gs}
sig_table = create_signaturemetadata_table()
head(sig_table)
```

### Signature

```{r}
create_signature_table()
```

### Citation

[Issue #6](https://github.com/seandavi/MungeCuratedMGS/issues/6)

```{r citation_table}
citation_table = create_citation_table()
head(citation_table)
```

### Study

```{r}
create_study_table()
```

### Contrast

```{r}
create_contrast_table()
```

### Citation

```{r}
create_citation_table()
```

## Write all tables as csv files

```{r, message=FALSE}
res <- write_all_tables()
names(res)
```

```{r}
    ## create keys
    study.string <- Reduce(paste, sheet[, study.cols])
    sheet$STUDY <-
        paste0("Study ", rank(study.string, ties.method = "min"))
    sheet$SIGNATURE <- create_keys("Signature ", nrow(sheet))
    ## create study sheet
    output <- list()
    output[["study"]] <- unique(sheet[, c("STUDY", study.cols)])
    output[["study"]]$DOI <- NA
    output[["study"]]$BibTex <- NA
    output[["study"]]$URI <- NA
    ## create signature sheet
    output[["signature"]] <-
        sheet[, !colnames(sheet) %in% colnames(output[["study"]])]
    output[["signature"]]$STUDY <- sheet$STUDY
    output[["signature"]] <-
        output[["signature"]][, !colnames(output[["signature"]]) %in% c("Dropbox", "PubMed")]
    output[["signature"]] <-
        output[["signature"]][,!sapply(output[["signature"]], function(x)
            all(is.na(x)))]
    return(output)
```

